Notation proposal

### 2011-05-31 notation.tex
notation: fix underbrace spacing
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@787 ccdd05d5-56c1-461a-bf98-85f6876523b4

\documentclass[letterpaper,11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{stmaryrd}

@@

Early-warning \textsc{snr}:
\begin{equation}
    \rho^{s}_i[k] = \underbrace{\sum_{l=0}^{L^{s}-1} v^{s}_{il} \sigma^{s}_l}_{\substack{\text{Reconstruction}\\ \text{with {\sc SVD}}}}
    \underbrace{\sum_{n=0}^{N^{s} - 1} u^{s}_{l}[n] x^{s}[k-n]}_{\substack{\text{orthogonal}\\ \text{{\sc FIR} filter}}} + \underbrace{\sum_{n=-N^\shortuparrow/2}^{N^\shortuparrow/2-1} b^\shortuparrow[n] \sum_{q \in \mathbb{Z}} \delta\!\left[k-n, q \frac{f^{s}}{f^{s+1}}\right]}_\text{interpolation filter} \underbrace{\rho^{s+1}_i[q]}_{\substack{\text{accumulated {\sc snr}}\\ \text{from prior time slices}}}
\end{equation}

>>>>

\documentclass[letterpaper,11pt]{article}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{stmaryrd}  % gives \shortuparrow and \shortdownarrow

@@

Early-warning \textsc{snr}:
\newcommand{\mystrut}{\rule[-2em]{0pt}{0pt}}
\begin{equation}
    \rho^{s}_i[k] = \underbrace{\mystrut\sum_{l=0}^{L^{s}-1} v^{s}_{il} \sigma^{s}_l}_{\substack{\text{Reconstruction}\\ \text{with {\sc SVD}}}}
    \underbrace{\mystrut\sum_{n=0}^{N^{s} - 1} u^{s}_{l}[n] x^{s}[k-n]}_{\substack{\text{orthogonal}\\ \text{{\sc FIR} filter}}} + \underbrace{\mystrut\sum_{n=-N^\shortuparrow/2}^{N^\shortuparrow/2-1} b^\shortuparrow[n] \sum_{q \in \mathbb{Z}} \delta\!\left[k-n, q \frac{f^{s}}{f^{s+1}}\right]}_\text{interpolation filter} \underbrace{\mystrut\rho^{s+1}_i[q]}_{\substack{\text{accum.}\\ \text{prior {\sc snr}}}}
\end{equation}
